Landscape heterogeneity simulation figures

### 2018-05-18 Manuscript_figures_2017_12_12.Rmd
Remove directory specific references

## Figure 1
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

## Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

@@

## Figure 2
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)

@@

## Figure S9
Random forest variable importance results from `party` package using cforest function
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

>>>>

## Figure 1
Random forest variable importance results
```{r}
library(randomForest)
#setwd()

@@

## Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
#setwd()

@@

#setwd()
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

@@

## Figure 2
Box plots rec rate vs. density
```{r}
#setwd()
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)

@@

## Figure S9
Random forest variable importance results from `party` package using cforest function
```{r}
#setwd()

@@

#setwd()
tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()
